### 2017-02-27 2017mergingmerges/section/XX-FutureWork.tex
Talk about Finite Streams last as it ends on a happier note

We now discuss some of the shortcomings of the system, and extensions and future work to ameliorate this.

@@

For a combinator such as @take@ which only needs a finite prefix of the input stream, it may be useful to add an instruction that allows a pulling process to explicitly disconnect from an input channel.
After disconnecting, the process no longer needs to be coordinated with the producer, leaving the producer free to push as often as the other consumers allow.

We have implemented an early prototype that supports finite streams, but further work is required to prove it correct.

It is also possible to encode finite streams as infinite streams with an explicit end-of-stream marker (EOF) and case statements. However, this requires the fusion transform to analyse and reason about case statements and their predicates. It seems obvious that if two consumers read the same value and check if it is EOF, they are both going to give the same result, but this is of course undecidable in general. By making the structure of finite streams explicit and constraining processes to use finite streams in particular ways, we may be able to give more guarantees than by relying on heuristics for deciding equality of predicates. Case analysis is still a useful extension and is described next.

@@

For example, suppose two processes have the same case condition (@x > 0@).
The fusion algorithm will generate all four possibilities, including the contradictory ones such as where the first process has (@x > 0 = true@) and the second has (@x > 0 = false@).
If any of these possibilities require an unbounded buffer, the fusion algorithm will fail.

A possible extension is to somehow cull these contradictory states so that if it is statically known that a state is unreachable, it does not matter if it requires unbounded buffers.
It may be possible to achieve this with relatively little change to the fusion algorithm itself, by having it emit some kind of failure instruction rather than failing to produce a process.
A separate postprocessing step could then perform analyses and remove statically unreachable process states.
After postprocessing, if any failure instructions are reachable, the fusion process would fail as before.

>>>>

% We now discuss some of the shortcomings of the system, and extensions and future work to ameliorate this.

For example, suppose two processes have the same case condition (@x > 0@).
The fusion algorithm will generate all four possibilities, including the contradictory ones such as where the first process has (@x > 0 = true@) and the second has (@x > 0 = false@).
If any require an unbounded buffer, the fusion algorithm will fail.

A possible extension is to somehow cull these contradictory states so that if it is statically known that a state is unreachable, it does not matter if it requires unbounded buffers.
It may be possible to achieve this with relatively little change to the fusion algorithm itself, by having it emit some kind of failure instruction rather than failing to produce a process.
A separate postprocessing step could then perform analyses and remove statically unreachable process states.
After postprocessing, if any failure instructions are reachable, fusion fails as before.

@@

For a combinator such as @take@ which only needs a finite prefix of the input stream, it may be useful to add an instruction that allows a pulling process to explicitly disconnect from an input channel. After disconnecting, the process no longer needs to be coordinated with the producer, leaving the producer free to push as often as the other consumers allow. We have implemented an early prototype that supports finite streams, our mechanized formalization does not cover it.

It is also possible to encode finite streams as infinite streams with an explicit end-of-stream marker (EOF) and case statements. However, this requires the fusion transform to analyse and reason about case statements and their predicates. It seems obvious that if two consumers read the same value and check if it is EOF, they are both going to give the same result, but this is of course undecidable in general. By making the structure of finite streams explicit and constraining processes to use finite streams in particular ways, we may be able to give more guarantees than by relying on heuristics for deciding equality of predicates.

@@
